Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-09 GHI_enh_03_process.tex
Commit 2024-05-10 00:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-19}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-384.81 -144.57  -53.50   96.68  768.76

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -9.187e+01  4.952e+01  -1.855   0.0644 .  
as.numeric(Date)  3.286e-07  3.958e-08   8.302 2.08e-15 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 211.4 on 361 degrees of freedom
Multiple R-squared:  0.1603,    Adjusted R-squared:  0.158 
F-statistic: 68.92 on 1 and 361 DF,  p-value: 2.077e-15
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-384.81 -144.57  -53.50   96.68  768.76

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -9.187e+01  4.952e+01  -1.855   0.0644 .  
ST_E_monthly$Date  3.286e-07  3.958e-08   8.302 2.08e-15 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 211.4 on 361 degrees of freedom
Multiple R-squared:  0.1603,    Adjusted R-squared:  0.158 
F-statistic: 68.92 on 1 and 361 DF,  p-value: 2.077e-15
\end{verbatim}

@@

\begin{verbatim}
aa
aday
All_daily_ratio_lim
alpha
ampl
avar
BIO_ELEVA
C1_Clearness_Kt_THRES
C1_GLB_diff_THRES
C2_Clearness_Kt_THRES
C3_cs_ref_ratio
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
C4_test_cs_ref_ratio
C4_test_GLB_diff_THRES
C4_test_lowcut_ratio
C4_test_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
variables_fl
yearstodo
ylim
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-04-19 10:26:46.8 athan@sagan GHI_enh_03_process.R 3.634787 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-09}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-327.56 -157.11  -65.36  116.74  760.36

Coefficients:
                  Estimate Std. Error t value Pr(>|t|)    
(Intercept)      2.431e+02  4.880e+01   4.981  9.8e-07 ***
as.numeric(Date) 6.397e-08  3.907e-08   1.637    0.102    
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 210.1 on 363 degrees of freedom
Multiple R-squared:  0.007332,  Adjusted R-squared:  0.004597 
F-statistic: 2.681 on 1 and 363 DF,  p-value: 0.1024
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-327.56 -157.11  -65.36  116.74  760.36

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)       2.431e+02  4.880e+01   4.981  9.8e-07 ***
ST_E_monthly$Date 6.397e-08  3.907e-08   1.637    0.102    
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 210.1 on 363 degrees of freedom
Multiple R-squared:  0.007332,  Adjusted R-squared:  0.004597 
F-statistic: 2.681 on 1 and 363 DF,  p-value: 0.1024
\end{verbatim}

@@

\begin{verbatim}
aa
aatm
aday
AEin1
All_daily_ratio_lim
alpha
amean
ampl
asza
atype
avar
b
BIO_ELEVA
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
C4_test_cs_ref_ratio
C4_test_GLB_diff_THRES
C4_test_lowcut_ratio
C4_test_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
fit
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
lm_mean
lm_zeropoint
mean_BR_mean
mean_BR_median
mean_BR_min
mean_mean
mean_median
mean_min
mid
MIN_ELEVA
MIN_N
mm
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
slope_mean
slope_median
slope_min
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
t
tsy
units
variables_fl
xlim
yearstodo
ylim
zeropoint
zeropointA
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-05-09 20:10:12.1 athan@sagan GHI_enh_03_process.R 3.712139 mins
\end{verbatim}

### 2024-05-09 GHI_enh_04_investigate.tex
Commit 2024-05-10 00:14

lmD: 1.552161 +/- 0.104876

lmY: 1.552176 +/- 0.104878

Arima: 1.552549 +/- 0.14034

@@

lmD: 0.954836 +/- 0.154734

lmY: 0.954859 +/- 0.154736

Arima: 1.024507 +/- 0.23503

@@

lmD: 1.088987 +/- 0.16743

lmY: 1.089013 +/- 0.167433

Arima: 1.160151 +/- 0.24838

@@

lmD: 1.050842 +/- 0.240164

lmY: 1.050851 +/- 0.240168

Arima: 1.050895 +/- 0.364666

@@

lmD: 0.958299 +/- 0.253655

lmY: 0.958309 +/- 0.25366

Arima: 0.958355 +/- 0.388216

@@

lmD: 1.089066 +/- 0.07424

lmY: 1.089079 +/- 0.074241

Arima: 1.089082 +/- 0.109498

@@

lmD: 1.136243 +/- 0.070602

lmY: 1.136256 +/- 0.070603

Arima: 1.136263 +/- 0.100583

@@

lmD: 33.75698 +/- 5.702807

lmY: 33.75752 +/- 5.702906

Arima: 33.816428 +/- 8.918367

@@

lmD: 0.003302 +/- 0.00027

lmY: 0.003302 +/- 0.00027

Arima: 0.003326 +/- 0.000357

@@

lmD: 0.001743 +/- 0.000278

lmY: 0.001743 +/- 0.000278

Arima: 0.001906 +/- 0.000459

@@

lmD: 0.001718 +/- 0.000312

lmY: 0.001718 +/- 0.000312

Arima: 0.001883 +/- 0.000503

@@

lmD: 0.001896 +/- 0.000307

lmY: 0.001896 +/- 0.000307

Arima: 0.001896 +/- 0.000479

@@

lmD: 0.001823 +/- 0.000299

lmY: 0.001823 +/- 0.000299

Arima: 0.001823 +/- 0.00046

@@

lmD: 0.002414 +/- 0.000233

lmY: 0.002414 +/- 0.000233

Arima: 0.002414 +/- 0.000362

@@

lmD: 0.002624 +/- 0.000228

lmY: 0.002624 +/- 0.000228

Arima: 0.002624 +/- 0.000339

@@

lmD: 0.988112 +/- 0.144355

lmY: 0.988134 +/- 0.144358

Arima: 1.051184 +/- 0.218585

@@

lmD: 0.816129 +/- 0.101923

lmY: 0.816139 +/- 0.101925

Arima: 0.816132 +/- 0.119665

@@

lmD: 0.215792 +/- 0.037414

lmY: 0.215795 +/- 0.037415

Arima: 0.215796 +/- 0.040986

@@

lmD: 0.181869 +/- 0.03711

lmY: 0.181874 +/- 0.037111

Arima: 0.181874 +/- 0.039209

@@

lmD: 0.481659 +/- 0.045723

lmY: 0.481664 +/- 0.045724

Arima: 0.481665 +/- 0.054201

@@

lmD: 0.001364 +/- 0.01878

lmY: 0.001365 +/- 0.018781

Arima: 0.001365 +/- 0.01932

@@

lmD: -0.018679 +/- 0.017374

lmY: -0.018679 +/- 0.017374

Arima: -0.018679 +/- 0.017837

@@

lmD: 0.496018 +/- 0.071855

lmY: 0.496024 +/- 0.071857

Arima: 0.496022 +/- 0.080622

@@

lmD: 0.597354 +/- 0.08202

lmY: 0.597361 +/- 0.082022

Arima: 0.597357 +/- 0.094227

@@

lmD: 1.432631 +/- 0.148944

lmY: 1.432652 +/- 0.148947

Arima: 1.432652 +/- 0.180994

@@

lmD: 0.001383 +/- 0.000137

lmY: 0.001383 +/- 0.000137

Arima: 0.001383 +/- 0.00016

@@

lmD: 0.00044 +/- 6.1e-05

lmY: 0.00044 +/- 6.1e-05

Arima: 0.00044 +/- 7e-05

@@

lmD: 0.000363 +/- 6.4e-05

lmY: 0.000363 +/- 6.4e-05

Arima: 0.000363 +/- 7.2e-05

@@

lmD: 4e-05 +/- 3.3e-05

lmY: 4e-05 +/- 3.3e-05

Arima: 4e-05 +/- 3.8e-05

@@

lmD: 5e-06 +/- 2.9e-05

lmY: 5e-06 +/- 2.9e-05

Arima: 5e-06 +/- 3.4e-05

@@

lmD: 0.000968 +/- 0.000108

lmY: 0.000968 +/- 0.000108

Arima: 0.000968 +/- 0.000125

@@

lmD: 0.001126 +/- 0.000119

lmY: 0.001126 +/- 0.000119

Arima: 0.001126 +/- 0.000138

@@

lmD: 0.036713 +/- 0.003659

lmY: 0.036714 +/- 0.003659

Arima: 0.036714 +/- 0.00425

@@

lmD: 0.203753 +/- 0.246152

lmY: 0.20379 +/- 0.246156

Arima: 0.191314 +/- 0.355242

@@

lmD: 0.066924 +/- 0.186933

lmY: 0.066947 +/- 0.186936

Arima: 0.031787 +/- 0.332858

@@

lmD: 0.108038 +/- 0.185587

lmY: 0.10806 +/- 0.18559

Arima: 0.07227 +/- 0.320898

@@

lmD: -0.047504 +/- 0.172428

lmY: -0.047493 +/- 0.17243

Arima: -0.093727 +/- 0.32618

@@

lmD: -0.06805 +/- 0.171992

lmY: -0.068039 +/- 0.171995

Arima: -0.113836 +/- 0.324815

@@

lmD: 0.1818 +/- 0.225799

lmY: 0.181836 +/- 0.225802

Arima: 0.164846 +/- 0.343081

@@

lmD: 0.192758 +/- 0.234509

lmY: 0.192794 +/- 0.234513

Arima: 0.178049 +/- 0.348128

@@

lmD: 0.372906 +/- 0.252445

lmY: 0.372932 +/- 0.252449

Arima: 0.373033 +/- 0.257109

@@

lmD: 0.000567 +/- 0.000291

lmY: 0.000567 +/- 0.000291

Arima: 0.000567 +/- 0.000322

@@

lmD: 0.000397 +/- 0.000226

lmY: 0.000397 +/- 0.000226

Arima: 0.000393 +/- 0.000269

@@

lmD: 0.000416 +/- 0.000234

lmY: 0.000416 +/- 0.000234

Arima: 0.000413 +/- 0.000274

@@

lmD: 0.000209 +/- 0.000208

lmY: 0.000209 +/- 0.000208

Arima: 0.000203 +/- 0.000261

@@

lmD: 0.000194 +/- 0.000208

lmY: 0.000194 +/- 0.000208

Arima: 0.000187 +/- 0.000261

@@

lmD: 0.000565 +/- 0.000272

lmY: 0.000565 +/- 0.000272

Arima: 0.000565 +/- 0.000304

@@

lmD: 0.000571 +/- 0.00028

lmY: 0.000571 +/- 0.00028

Arima: 0.000571 +/- 0.000312

@@

lmD: 0.008989 +/- 0.005522

lmY: 0.008989 +/- 0.005522

Arima: 0.009015 +/- 0.00575

@@

Arima: 0.215796 +/- 0.040986

@@

\begin{verbatim}
Warning: Removed 25 rows containing missing values or values outside the scale
range (`geom_bar()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 16 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

lmY: 339.1753 +/- 35.87673

@@

lmY: 123.4768 +/- 11.47021

@@

lmY: 0.228163 +/- 0.054288

@@

lmY: 0.174806 +/- 0.039192

@@

\begin{verbatim}
2024-04-19 10:28:33.6 athan@sagan GHI_enh_04_investigate.R 0.788870 mins
\end{verbatim}

>>>>

lmD: 0.56672 +/- 0.105912

lmY: 0.566719 +/- 0.105914

Arima: 0.567051 +/- 0.141823

@@

lmD: -0.300529 +/- 0.154885

lmY: -0.300528 +/- 0.154888

Arima: -0.2336 +/- 0.235583

@@

lmD: -0.247556 +/- 0.167713

lmY: -0.247553 +/- 0.167716

Arima: -0.179333 +/- 0.249282

@@

lmD: -0.450424 +/- 0.239956

lmY: -0.450441 +/- 0.23996

Arima: -0.450398 +/- 0.364663

@@

lmD: -0.558109 +/- 0.253332

lmY: -0.558126 +/- 0.253337

Arima: -0.55808 +/- 0.388026

@@

lmD: 0.234369 +/- 0.074603

lmY: 0.234366 +/- 0.074604

Arima: 0.234368 +/- 0.110217

@@

lmD: 0.302033 +/- 0.07107

lmY: 0.302031 +/- 0.071072

Arima: 0.302035 +/- 0.101344

@@

lmD: -12.24511 +/- 5.698072

lmY: -12.24538 +/- 5.698171

Arima: -12.195036 +/- 8.900074

@@

lmD: 0.00134 +/- 0.000272

lmY: 0.00134 +/- 0.000272

Arima: 0.001363 +/- 0.00036

@@

lmD: 0.000403 +/- 0.000279

lmY: 0.000403 +/- 0.000279

Arima: 0.000564 +/- 0.000462

@@

lmD: 0.000343 +/- 0.000314

lmY: 0.000343 +/- 0.000314

Arima: 0.000504 +/- 0.000507

@@

lmD: 0.000941 +/- 0.000309

lmY: 0.000941 +/- 0.000309

Arima: 0.000941 +/- 0.000482

@@

lmD: 0.000981 +/- 0.000301

lmY: 0.000982 +/- 0.000301

Arima: 0.000982 +/- 0.000462

@@

lmD: 0.000734 +/- 0.000235

lmY: 0.000734 +/- 0.000235

Arima: 0.000734 +/- 0.000366

@@

lmD: 0.000872 +/- 0.000229

lmY: 0.000872 +/- 0.000229

Arima: 0.000872 +/- 0.000342

@@

lmD: 0.180964 +/- 0.145233

lmY: 0.180972 +/- 0.145235

Arima: 0.238782 +/- 0.22021

@@

lmD: 0.127247 +/- 0.099723

lmY: 0.127245 +/- 0.099725

Arima: 0.127249 +/- 0.115059

@@

lmD: 0.065571 +/- 0.036505

lmY: 0.065571 +/- 0.036506

Arima: 0.065573 +/- 0.04

@@

lmD: 0.085245 +/- 0.036172

lmY: 0.085246 +/- 0.036173

Arima: 0.085247 +/- 0.038483

@@

lmD: 0.015901 +/- 0.044784

lmY: 0.015898 +/- 0.044784

Arima: 0.015898 +/- 0.052937

@@

lmD: 0.033836 +/- 0.018543

lmY: 0.033837 +/- 0.018543

Arima: 0.033838 +/- 0.01905

@@

lmD: 0.03242 +/- 0.017152

lmY: 0.032421 +/- 0.017152

Arima: 0.032421 +/- 0.017569

@@

lmD: 0.074226 +/- 0.070335

lmY: 0.074225 +/- 0.070336

Arima: 0.074226 +/- 0.077768

@@

lmD: 0.087786 +/- 0.080412

lmY: 0.087785 +/- 0.080413

Arima: 0.087788 +/- 0.090783

@@

lmD: 0.071192 +/- 0.144022

lmY: 0.071187 +/- 0.144025

Arima: 0.071193 +/- 0.173121

@@

lmD: 0.000213 +/- 0.000135

lmY: 0.000213 +/- 0.000135

Arima: 0.000213 +/- 0.000155

@@

lmD: 0.000117 +/- 5.9e-05

lmY: 0.000117 +/- 5.9e-05

Arima: 0.000117 +/- 6.8e-05

@@

lmD: 0.000135 +/- 6.2e-05

lmY: 0.000135 +/- 6.2e-05

Arima: 0.000135 +/- 6.9e-05

@@

lmD: 5.8e-05 +/- 3.1e-05

lmY: 5.8e-05 +/- 3.1e-05

Arima: 5.8e-05 +/- 3.6e-05

@@

lmD: 5.3e-05 +/- 2.8e-05

lmY: 5.3e-05 +/- 2.8e-05

Arima: 5.3e-05 +/- 3.2e-05

@@

lmD: 0.000174 +/- 0.000106

lmY: 0.000174 +/- 0.000106

Arima: 0.000174 +/- 0.000121

@@

lmD: 0.000194 +/- 0.000116

lmY: 0.000194 +/- 0.000116

Arima: 0.000194 +/- 0.000134

@@

lmD: 0.001754 +/- 0.003555

lmY: 0.001754 +/- 0.003556

Arima: 0.001754 +/- 0.00409

@@

lmD: -1.406706 +/- 0.24506

lmY: -1.406695 +/- 0.245065

Arima: -1.417205 +/- 0.351582

@@

lmD: -1.527566 +/- 0.186094

lmY: -1.527568 +/- 0.186097

Arima: -1.558334 +/- 0.32687

@@

lmD: -1.488694 +/- 0.184965

lmY: -1.488697 +/- 0.184968

Arima: -1.520192 +/- 0.31545

@@

lmD: -1.626611 +/- 0.17175

lmY: -1.626625 +/- 0.171753

Arima: -1.666679 +/- 0.318198

@@

lmD: -1.642527 +/- 0.171263

lmY: -1.642542 +/- 0.171266

Arima: -1.682227 +/- 0.316737

@@

lmD: -1.425903 +/- 0.224826

lmY: -1.425893 +/- 0.22483

Arima: -1.440441 +/- 0.339186

@@

lmD: -1.416548 +/- 0.23349

lmY: -1.416538 +/- 0.233494

Arima: -1.429067 +/- 0.34436

@@

lmD: 0.057623 +/- 0.247504

lmY: 0.057642 +/- 0.247508

Arima: 0.05775 +/- 0.252236

@@

lmD: -0.001993 +/- 0.000291

lmY: -0.001994 +/- 0.000291

Arima: -0.001994 +/- 0.000321

@@

lmD: -0.002127 +/- 0.000226

lmY: -0.002127 +/- 0.000226

Arima: -0.002131 +/- 0.000268

@@

lmD: -0.002106 +/- 0.000234

lmY: -0.002106 +/- 0.000234

Arima: -0.00211 +/- 0.000274

@@

lmD: -0.002288 +/- 0.000208

lmY: -0.002288 +/- 0.000208

Arima: -0.002296 +/- 0.000261

@@

lmD: -0.0023 +/- 0.000208

lmY: -0.0023 +/- 0.000208

Arima: -0.002309 +/- 0.000261

@@

lmD: -0.001986 +/- 0.000271

lmY: -0.001986 +/- 0.000271

Arima: -0.001986 +/- 0.000303

@@

lmD: -0.001985 +/- 0.00028

lmY: -0.001985 +/- 0.00028

Arima: -0.001985 +/- 0.000311

@@

lmD: 0.000428 +/- 0.005409

lmY: 0.000428 +/- 0.005409

Arima: 0.000453 +/- 0.005642

@@

Arima: 0.065573 +/- 0.04

@@

\begin{verbatim}
Warning: Removed 23 rows containing missing values or values outside the scale
range (`geom_bar()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 18 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

lmY: 50.70791 +/- 35.58152

@@

lmY: 20.14994 +/- 11.43911

@@

lmY: 0.032227 +/- 0.053277

@@

lmY: 0.036732 +/- 0.039744

@@

\begin{verbatim}
2024-05-09 20:12:01.6 athan@sagan GHI_enh_04_investigate.R 0.834317 mins
\end{verbatim}

### 2024-05-09 article/article.tex
Commit 2024-05-10 00:14

Our dataset, after the data selection processing, consists of 6144534
records of GHI, of which \(1.592\,\%\) are CE and \(0.036\,\%\) are ECE
events. The highest GHI recorder was \(1416.6\,W/m^2\) on 24~May 2007.
The absolute stronger CE event had an OIR of \(335.28\,W/m^2\) on 24~May
2007. The relative stronger CE event was \(50.2\,\%\) above the clear
sky threshold, on 28~October 2016.

@@

We computed the daily trend of the mean OIR of CE
(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order
autoregressive model with lag of 1 day, using the `maximum likelihood'
fitting method \citep{Gardner1980, Jones1980} by implementing the
function `arima' from the library `stats' of the R programming language
\citep{RCT2023}. The trends are reported together with the \(2\sigma\)
error. We observe an increase of \(0.202\pm 0.083\,W/m^2/y\) on the mean
OIR.

@@

Although, the previous result is closer to the raw data, we preferred to
present the annual statistics, that give a more clear picture about the
long term CE trends. Hence, we calculated the annual values from the
one-minute measurements. The trend of OIR is \(0.22\pm 0.11\,W/m^2/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-mean}), but this value alone is
not very useful due the intrinsic high variability of this metric.

@@

A better indicator of changes on the characteristic of CE would be the
number of CE occurrences and the total energy of the CE over irradiance.
The annual number of CE occurrences, shows a steady increase of
\(110.1\pm 20.3\,\text{cases}/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-N}). We have to note that the
energy related to the CE events can not be directly linked with the
total energy balance on the atmosphere. The net sun radiation of the
region is not increased, but rather redistributed through the CE.
Although, the instantaneous values, can exceed the equivalent clear sky
irradiance to a considerable level.

@@

Subsequently, the mean annual increase of energy due to CE events is
\(293.3\pm 63.1\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
the trend of the number of occurrences.

@@

In order to further study the characteristics of the CE events, we
grouped the single minute CE events, to continuous CE groups (CEG).
Thus, a CEG consists of one or more successive CE cases, and can have a
duration of multiple of minutes. We have identified 26042 groups, where
the group with the longest duration lasted 140 minutes on 07~July 2013.
By examining the frequency distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can
conclude that longer durations are getting increasingly rare, with
durations above 10 minutes very rare.

>>>>

Our dataset, after the data selection processing, consists of 6144534
records of GHI, of which \(1.906\,\%\) are CE and \(0.036\,\%\) are ECE
events. The highest GHI recorder was \(1416.6\,W/m^2\) on 24~May 2007.
The absolute stronger CE event had an OIR of \(353.46\,W/m^2\) on
21~June 2001. The relative stronger CE event was \(49.9\,\%\) above the
clear sky threshold, on 28~October 2016.

@@

We computed the daily trend of the mean OIR of CE
(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order
autoregressive model with lag of 1 day, using the `maximum likelihood'
fitting method \citep{Gardner1980, Jones1980} by implementing the
function `arima' from the library `stats' of the R programming language
\citep{RCT2023}. The trends are reported together with the \(2\sigma\)
error. We observe an increase of \(0.066\pm 0.08\,W/m^2/y\) on the mean
OIR.

@@

Although, the previous result is closer to the raw data, we preferred to
present the annual statistics, that give a more clear picture about the
long term CE trends. Hence, we calculated the annual values from the
one-minute measurements. The trend of OIR is \(0.03\pm 0.11\,W/m^2/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-mean}), but this value alone is
not very useful due the intrinsic high variability of this metric.

@@

A better indicator of changes on the characteristic of CE would be the
number of CE occurrences and the total energy of the CE over irradiance.
The annual number of CE occurrences, shows a steady increase of
\(20.1\pm 22.9\,\text{cases}/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-N}). We have to note that the
energy related to the CE events can not be directly linked with the
total energy balance on the atmosphere. The net sun radiation of the
region is not increased, but rather redistributed through the CE.
Although, the instantaneous values, can exceed the equivalent clear sky
irradiance to a considerable level.

@@

Subsequently, the mean annual increase of energy due to CE events is
\(50.7\pm 71.2\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
the trend of the number of occurrences.

@@

In order to further study the characteristics of the CE events, we
grouped the single minute CE events, to continuous CE groups (CEG).
Thus, a CEG consists of one or more successive CE cases, and can have a
duration of multiple of minutes. We have identified 30221 groups, where
the group with the longest duration lasted 140 minutes on 07~July 2013.
By examining the frequency distribution of the CEG durations
(Figure\nobreakspace{}\ref{fig:ceg-duration-distribution}), we can
conclude that longer durations are getting increasingly rare, with
durations above 10 minutes very rare.
